Modelling Weddell Sea Food Web

### 2022-02-09 ModellingWeddellSea.Rmd
Update interaction dimensionality to calculate calc_weighted_topological_indices

# Extract the birds from the network
#
# require(taxize)
# can_names <- gnr_resolve(unique(wedd_df$con.taxonomy), best_match_only = TRUE, canonical=TRUE)
# class_names <- tax_name(query =can_names$matched_name2  , get = "class", db = "ncbi")
# aves <- class_names %>% filter( class =="Aves")
# 
# wedd_df %>% filter(con.taxonomy=="Fulmarus glacialoides") %>% select(con.mass.mean.g.)

@@

wedd_int <- interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )

#wedd_df <- wedd_df %>% mutate(res.mass.mean.g.=ifelse(res.mass.mean.g.==-9.99e+02, 1e-14, res.mass.mean.g.))

@@

ave.image()

>>>>

@@

#
# Update by hand the missing interaction_dim to a new file called ---> "Data/Wedd_mass_complete.dat"
#

wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ")

#
# Calculate interaction intensity
#
wedd_int <- interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )

@@

save.image()

#
# Convert to an igraph with weights
#

g <- graph_from_data_frame(wedd_int %>% select(res_taxonomy,con_taxonomy,qRC) %>% rename(weight=qRC) ,directed=TRUE)   # the 3d field generate an attribute
E(g)$weight

calc_weighted_topological_indices(g)
calc_topological_indices(g)
